---
title: Will Adrian Martinez Satisfy K-State Fans?
author: Natalie Frick
date: '2022-04-06'
slug: will-adrian-martinez-satisfy-k-state-fans
categories: []
tags: []
---
```{r warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)
library(ggalt)
library(scales)
library(waffle)
```
After spending four years at the University of Nebraska-Lincoln, quarterback Adrian Martinez decided to enter the transfer portal and continue his athletic career at Kansas State University. 

Skylar Thompson, the QB for K-State since 2017, created quite the fan base among Wildcat fans during his five seasons. Thompson's last year of eligibility with Kansas State was 2021. 

Now, Nebraska and Kansas State fans are curious about how the two quarterbacks will compare and where Martinez will land measured next to other Big 12 quarterbacks. 
```{r warning=FALSE, message=FALSE, echo=FALSE}
adrian <- read_csv("adrianmartinez.csv")
skylar <- read_csv("skylarthompson.csv")
skylar2021 <- skylar %>% filter(Year == "2021")
adrian2021 <- adrian %>% filter(Year == "2021")
big12QB2021 <- read_csv("Big12QBs.csv")
```
```{r warning=FALSE, message=FALSE, echo=FALSE}
alldata <- bind_rows(big12QB2021, adrian2021, skylar2021)
```
```{r warning=FALSE, message=FALSE, echo=FALSE}
ggplot() + 
  geom_bar(data=alldata, aes(x=reorder(School, `PassingTD`), weight=`PassingTD`)) +
  scale_y_continuous(labels=comma) +
  coord_flip() +
  labs(title="Martinez and Thompson are Extremely Comparable", subtitle="According to thier 2021 seasons passing touchdowns, they come out right next to each other." , x="School", y="Passing TD's", caption="Source: Sports-Reference.com | By Natalie Frick") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 10), 
    plot.subtitle = element_text(size=10), 
    panel.grid.minor = element_blank()
    )
```
```{r warning=FALSE, message=FALSE, echo=FALSE}
big12allyears <- read_csv("Big12AllYears.csv")
big10allyears <- read_csv("Big10AllYears.csv")
big102021 <- big10allyears %>% filter(Year == "2021")
```
TEXT HERE
```{r warning=FALSE, message=FALSE, echo=FALSE}
ggplot() + 
  geom_point(data=big12QB2021, aes(x=PassingAtt, y=PassingYds), color="grey") +
  geom_point(data=big102021, aes(x=PassingAtt, y=PassingYds), color="grey") +
  geom_point(data=skylar2021, aes(x=PassingAtt, y=PassingYds), color="purple") + 
  geom_point(data=adrian2021, aes(x=PassingAtt, y=PassingYds), color="red") +
  geom_text(data=skylar2021, aes(x=PassingAtt-.03, y=PassingYds+4, label = School)) +
  geom_text(data=adrian2021, aes(x=PassingAtt-.03, y=PassingYds+4, label = School)) +
  labs(title="Two Quarterbacks in the Midwest, Who are Extremly Mid", subtitle="Martinez and Thompson fall right next to each other again - right in the middle of the pack." , x="Passing Yards", y="Passing Attempts",caption="Source: Sports-Reference.com | By Natalie Frick") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 10), 
    plot.subtitle = element_text(size=10), 
    panel.grid.minor = element_blank()
    )
```
TEXT HERE 

```{r warning=FALSE, message=FALSE, echo=FALSE}
adriangamelogs2021 <- read_csv("adrianmartinez2021season.csv")
skylargamelogs2021 <- read_csv("skylarthompson2021season.csv")
oklahomastate <- read_csv("OklahomaState2021.csv")
baylor <- read_csv("baylor2021.csv")
oklahoma <- read_csv("oklahoma2021.csv")
iowastate <- read_csv("IowaState2021.csv")
westvirginia <- read_csv("WestVirginia2021.csv")
texastech <- read_csv("TexasTech2021.csv")
texas2021 <- read_csv("Texas2021.csv")
tcu2021 <- read_csv("TCU2021.csv")
kansas2021 <- read_csv("Kansas2021.csv")
```
```{r warning=FALSE, message=FALSE, echo=FALSE}
ggplot() + 
  
  geom_step(data=oklahomastate, aes(x=Date, y=PassingAtt, group=School), color="grey") +
  geom_step(data=baylor, aes(x=Date, y=PassingAtt, group=School), color="grey") +
  geom_step(data=oklahoma, aes(x=Date, y=PassingAtt, group=School), color="grey") +
  geom_step(data=iowastate, aes(x=Date, y=PassingAtt, group=School), color="grey") +
  geom_step(data=westvirginia, aes(x=Date, y=PassingAtt, group=School), color="grey") +
  geom_step(data=texastech, aes(x=Date, y=PassingAtt, group=School), color="grey") +
  geom_step(data=texas2021, aes(x=Date, y=PassingAtt, group=School), color="grey") +
  geom_step(data=tcu2021, aes(x=Date, y=PassingAtt, group=School), color="grey") +
  geom_step(data=kansas2021, aes(x=Date, y=PassingAtt, group=School), color="grey") +
  geom_step(data=skylargamelogs2021, aes(x=Date, y=PassingAtt, group=School), color="purple") + 
  geom_step(data=adriangamelogs2021, aes(x=Date, y=PassingAtt, group=School), color="red") +
  labs(title="Martinez is More Consistant", subtitle="When it comes to passing attempts per game, Martinez is more reliable." , x="Games", y="Passing Attempts",caption="Source: Sports-Reference.com | By Natalie Frick") +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 16, face = "bold"),
    axis.title = element_text(size = 10), 
    plot.subtitle = element_text(size=10), 
    panel.grid.minor = element_blank()
    )
```

